Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/experiments.tex

In all settings, we use the learning algorithm described in
Alg.~\ref{alg:dau} and \TODO{supplementary, algo 1}. The variants of DDPG and DQN
used are described in the supplementary material, as well as all the hyperparameters
used. To make comparison fair, we use the properly rescaled discount
factor $\gamma_\deltat$ and reward $r_\deltat$ from \eqref{eq:def-gamma}, as well as scaled learning rates, for DDPG and DQN.

Let us stress that quantities shown are rescaled to make comparison possible. For example,
return results are given in term of discretized return $R_\deltat$ as defined in Eq. \eqref{eq:discretized-return},\footnote{This mostly amounts to scaling rewards
by a factor $\deltat$ when this scaling is not naturally done in the environment. Environment specific
details are given in the supplementary material.} and, most notably, time elapsed is always given in
normalized epochs, i.e. the true number of epochs multiplied by the discretization timestep.

>>>>

In all settings, we use the learning algorithm described in
Alg.~\ref{alg:dau} and \TODO{supplementary, algo 1}. The variants of DDPG and DQN
used are described in the supplementary material, as well as all the hyperparameters
used. To make comparison fair, we use the properly rescaled discount
factor $\gamma_\deltat$ and reward $r_\deltat$ from \eqref{eq:def-gamma},
as well as scaled learning rates, for DDPG and DQN. \TODO{NDY not
convincing: precisely because DDPG and DQN are not invariant, they might
benefit from a different scaling.}

Let us stress that the quantities plotted are rescaled to make comparison
possible across different timesteps. For example,
return results are given in term of discretized return $R_\deltat$ as defined in \eqref{eq:discretized-return},\footnote{This mostly amounts to scaling rewards
by a factor $\deltat$ when this scaling is not naturally done in the environment. Environment-specific
details are given in the supplementary material.} and, most notably, time elapsed is always given in
normalized epochs (physical time), i.e. the true number of epochs multiplied by the
discretization timestep.
